### 2021-06-09 letter/responseLetter.tex

\begin{document}

\begin{letter}{JSS Editors,}
\opening{The comments of the reviewers have been very useful. They made us aware that some important points we were trying to convey remained obscure. We have corrected infelicities of presentation and all errors that the reviewers brought to our attention. The text in {\color{blue}blue} indicates how we have dealt with each individual comment.}

{\bf Reviewer 1}

\begin{itemize}
\item In the first place, what I missed is an overview of the empirical studies conducted and the relation between 
first and second experiment. I would recommend to include, before Sections 3.2 and 3.3, a section 
presenting the overall research methodology and the connections between the studies - in this sense, 
a figure reporting the various steps would be appreciated; Figure 2 only summarizes the design of the first study.

@@

\vspace{0.2cm}

{\color{blue}{\bf Answer.} answer}

\vspace{0.2cm}

\item In the second place, I would recommend to include more details on the experiments conducted. This is especially 
true for the second study, where Section 3.3 is a bit shallow. The three steps of the methodology are indeed shortly 
described without providing enough details, hence possibly precluding verifiability and replicability. In addition, the 
methodology is not linked to the research questions: I would recommend to restructure Section 3 in order to have 
data extraction processes and data analysis procedures for each research question.

@@

\vspace{0.2cm}

\item In 3.3, you mentioned ``we investigate whether or not a more advanced static analysis approach is promising for mining 
Android sandboxes. To this end, we leverage the FlowDroid taint analysis algorithms...''. True, FlowDroid has its edge 
in privacy leakage detection, but what's your justification for saying FlowDroid is more advanced in terms of static analysis?

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Thanks for raising this question. Here we were intended to say that FlowDroid implements a more advanced static analysis approach than DroidFax. We agree that the sentence is ambiguous, and we fixed that in the new version of the paper (first paragraph
  of section 3.3).}

@@

\vspace{0.2cm}

\item By definition, mining sandboxes means a technique to confine an application to resources accessed during automatic 
testing [1]. But in 3.3, you are comparing the source-sink pairs between that of a benign app and its malign twin. It is already 
not ``Mining Sandboxes''.

\vspace{0.2cm}

{\color{blue}{\bf Answer.} We totally agree. We changed the title of Section 3.3 and fixed this wrong misconception related to our taint analysis usage, which is used not for mining sandboxes but rather as an alternative approach for identifying malware. Fixing this issue required modifications not only in Section 3.3 but also in many other parts of the paper (including Abstract, Introduction, and Results). Many thanks for raising this issue.}

\item Also, FlowDroid requires as input the sources and sinks APIs. But you mine ``all sources and sinks 
paths''. Do you mean all APIs? FlowDroid will never finish running. 
\vspace{0.2cm}

{\color{blue}{\bf Answer.} You are right: we actually use a set of sensitive sources and sinks. We changed the second paragraph of Section 3.3 to clarify this point. Thanks. We hope that the current version of our paper fixes this misunderstanding.}

\item Assume a set of sensitive sources and sinks are selected, 
FlowDroid is already good in suggesting which one is malign by revealing info flows. What's the point of applying [1]'s setting?

{\color{blue}{\bf Answer.} Our idea in the second study is to find divergences in the info flows when considering two executions of FlowDroid: one execution using the benign version and one execution using the malicious version. The source-sink paths collected in the first execution of FlowDroid (benign version)
 {\bf are not considered suspicious}. Only the paths in the second execution, which do not appear in the first execution, are considered suspect and are used to point out the malware. We changed Section 3.3 to detail our approach better.}

{\color{blue}{\bf Answer.} answer}

### 2021-06-09 setup.tex
updates on the response letter to address R2C3

In the second study 
we investigate whether or not a more advanced static analysis approach is promising for
identifying malwares, given a version of an app that is proved to be secure.
To this end, we leverage the FlowDroid
taint analysis algorithms for Android apps, in order to identify dataflows
that might lead to the leakage of sensitive information. Our
goal here is to investigate if it is possible to detect malicious
behavior by identifying the \emph{divergent} source-sink paths that FlowDroid reveals after
analysing a benign and a malign versions of an Android app.
define.

>>>>

In the second study 
we investigate whether or not taint-based static analysis approach is also promising for
identifying malwares, given a version of an app that is proved to be secure.
To this end, we leverage the FlowDroid
taint analysis algorithms for Android apps, in order to identify dataflows
that might lead to the leakage of sensitive information. Our
goal here is to investigate if it is possible to detect malicious
behavior by identifying the \emph{divergent} source-sink paths that FlowDroid reveals after
analysing a benign and a malign versions of an Android app.
define.
